Network Origins of Social Distinction

### 2025-09-14 manuscript.tex
Updates from Overleaf

\begin{figure}[ht!]
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/star.png}
            \caption{Star Graph}
            \label{fig:star}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle.png}
            \caption{Circle Graph}
            \label{fig:circle}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/kite.png}
            \caption{Kite Graph}
            \label{fig:kite}
    \end{subfigure}
    \caption{Distinction Centrality in toy graphs. Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
\end{figure}

\input{Tabs/circle}

@@

\input{Tabs/clique}
%Clique addition experiment
%Add cliques to star graph and see what happens
%See what happens with the caveman

@@

@@

%https://journals.aps.org/pre/abstract/10.1103/PhysRevE.71.056103

\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-triangle1.png}
            \caption{Circle Graph with Near Neighbor Closure}
            \label{fig:circletriangle}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-long.png}
            \caption{Circle Graph with Long Tie}
            \label{fig:circlelong}
    \end{subfigure} \\
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/start-triangle1.png}
            \caption{Star Graph with Near Neighbor Closure}
            \label{fig:startriangle1}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/start-triangle2.png}
            \caption{Star Graph with Two Triangles}
            \label{fig:startriangle2}
    \end{subfigure}
    \caption{Distinction Centrality in toy graphs. Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
    \label{fig:toys}
\end{figure}

\input{Tabs/circletriangle}
\input{Tabs/circlelong}
\input{Tabs/kite}

\input{Tabs/structfold.tex}
\input{Tabs/intraclust}
\input{Tabs/interclust}
\input{Tabs/clique}

@@

\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/broker3.png}
            \caption{Brokerage Mediated (3-Cliques)}
            \label{fig:classicbrokerage3}
    \end{subfigure} 
     \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf4.png}
            \caption{Structural Fold (4-Clique)}
            \label{fig:sf}
    \end{subfigure} 
    \label{fig:struct-fold}
     \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/broker4.png}
            \caption{Brokerage Mediated (4-Cliques)}
            \label{fig:classicbrokerage3}
    \end{subfigure} 
     \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf5.png}
            \caption{Structural Fold (5-Clique)}
            \label{fig:sf}
    \end{subfigure} 
    \label{fig:struct-fold}
    \caption{Comparison of betweenness brokerage and a structural fold goes here}
\end{figure}

\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator2.png}
            \caption{Mediator between two trees with two branches (2, 2, 2)}
            \label{fig:treemediator2}
    \end{subfigure} 
    \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator3.png}
            \caption{Mediator between two trees with three branches (2, 3, 2)}
            \label{fig:treemediator3}
    \end{subfigure}
    \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator2-long.png}
            \caption{Mediator between two trees with two branches (2, 2, 2) with long tie}
            \label{fig:treemediatorlong2}
    \end{subfigure}
    \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator3-long.png}
            \caption{Mediator between two trees with three branches (2, 2, 2) with long tie}
            \label{fig:treemediatorlong3}
    \end{subfigure}
    \label{fig:struct-folds}
    \caption{Examples of varying parameters of mediator brokerage in tree graphs (Burt brokerage). Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
\end{figure}

\begin{figure}
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/two-connected.png}
            \caption{Two-Connected}
            \label{fig:twoconnected}
    \end{subfigure} 
    \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-weld.png}
            \caption{Circle Weld}
            \label{fig:circleweld}
    \end{subfigure}
    \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/two-connected-long.png}
            \caption{2-Connected Subgraphs with Long Tie}
            \label{fig:twoconnectedlong}
    \end{subfigure}
    \begin{subfigure}[b]{0.35\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel.png}
            \caption{Wheel Graph}
            \label{fig:wheel}
    \end{subfigure}
    \label{fig:struct-folds}
    \caption{Examples of varying degrees of connectedness within welded subgraphs. Distinction Centrality in toy graphs. Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
\end{figure}

@@

@@

\input{Tabs/political.tex}

>>>>

\begin{figure}[ht!]
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/star.png}
            \caption{Star Graph}
            \label{fig:star}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle.png}
            \caption{Circle Graph}
            \label{fig:circle}
    \end{subfigure}
    \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/clique.png}
            \caption{Clique Graph}
            \label{fig:clique}
    \end{subfigure}
    \caption{Distinction Centrality in toy graphs. Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
\end{figure}

@@

%Clique addition experiment
%Add cliques to star graph and see what happens
%See what happens with the caveman

@@

%triadic closure graphs
\begin{figure}[t!]
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-triangle1.png}
            \caption{Circle Graph with Near Neighbor Closure}
            \label{fig:circletriangle}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-long.png}
            \caption{Circle Graph with a Long Tie}
            \label{fig:circlelong}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/star-triangle1.png}
            \caption{Star Graph with Near Neighbor Closure}
            \label{fig:startriangle1}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/star-triangle2.png}
            \caption{Star Graph with Two Triangles}
            \label{fig:startriangle2}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/two-connected-long.png}
            \caption{2-Connected Subgraphs with Long Tie}
            \label{fig:twoconnectedlong}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/wheel.png}
            \caption{Wheel Graph, 6 Triads}
            \label{fig:wheel}
    \end{subfigure}
    \caption{Distinction Centrality in toy graphs. Nodes with the highest distinction are shown in red, nodes with positive distinction are shown in blue, nodes with negative distinction are shown in tan, and nodes with distinction close to zero are shown in purple.}
\end{figure}

%triadic closure centrality scores
\input{Tabs/Figure3}

%https://journals.aps.org/pre/abstract/10.1103/PhysRevE.71.056103
%\input{Tabs/intraclust}
%\input{Tabs/interclust}

@@

@@

%brokerage and structural folds Figure 4
\begin{figure}[H]
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf4.png}
            \caption{Structural Fold (4-Clique)}
            \label{fig:sf}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/sf5.png}
            \caption{Structural Fold (5-Clique)}
            \label{fig:sf}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/two-connected.png}
            \caption{Two-Connected}
            \label{fig:twoconnected}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/circle-weld.png}
            \caption{Circle Weld}
            \label{fig:circleweld}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/broker3.png}
            \caption{Brokerage Mediated (3-Cliques)}
            \label{fig:classicbrokerage3}
    \end{subfigure} 
    \label{fig:struct-fold}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/broker4.png}
            \caption{Brokerage Mediated (4-Cliques)}
            \label{fig:classicbrokerage3}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator2.png}
            \caption{Tree with 2 Branches, 2 Leaves}
            \label{fig:treemediator2}
    \end{subfigure} 
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator3.png}
            \caption{Tree with 2 Branches, 3 Leaves}
            \label{fig:treemediator3}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator2-long.png}
            \caption{Tree with 2 Branches, 2 Leaves, 1 Long Tie}
            \label{fig:treemediatorlong2}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/Toys/tree-mediator3-long.png}
            \caption{Tree with 2 Branches, 3 Leaves, 1 Long Tie}
            \label{fig:treemediatorlong3}
    \end{subfigure}
    \caption{Comparison of betweenness brokerage and a structural fold goes here}
\end{figure}

%brokerage centrality scores
\input{Tabs/Figure4}

@@

\input{Tabs/Figure5(kites)}

@@

\input{Tabs/Figure6.tex}
